### 2013-06-14 tex/execution.tex
Refined the definitions, added more math symbols

\subsection{Write}
The write instruction takes three arguments: a reference $r$, a field $f$, and a value $v$. If $r$ is a symbolic location, then the target field is written with the value directly. If $r$ is a symbolic reference, write proceeds as follows:
\begin{compactenum}
\item Resolve a list of feasible targets.
\item Access the fields of the feasible targets, performing a conditional write. The conditional write works by modifying the constraint equation as follows:
\newline  ((A==h_n) => F==V) and (~(A==h_n) => Eqn_o_l_d)
\end{compactenum}

\subsection{Arithmetic Instructions}
\subsection{Object Creation/Manipulation Instructions}
\subsection{Control Transfer Instructions}
\subsection{Assume / Assert Instructions}

>>>>

\subsection{Write}
The write instruction takes three arguments: a reference $r$, a field $f$, and a value $v$. If $r$ is a symbolic location, then the target field is written with the value directly. If $r$ is a symbolic reference, write proceeds as follows:
\begin{compactenum}
\item Resolve a list of feasible targets.
\item Access the fields of the feasible targets, performing a conditional write. The conditional write works by modifying the constraint equation as follows:
\begin{equation}
  ((r\rightarrow h_n) \Rightarrow f\rightarrow v)  \wedge (\lnot (r\rightarrow h_n) \Rightarrow Eqn_o_l_d)
\end{equation}
\end{compactenum}

\subsection{Arithmetic Instructions}
\subsection{Object Creation/Manipulation Instructions}
\subsection{Control Transfer Instructions}
Control transfer instructions are those instructions that have a "branching" nature. They are instructions that have more than one possible program location successor. Control transfer instructions are executed by comparing the compare condition to the constraints contained in the symbolic store. Those values in the store for which the constraints are now infeasible are eliminated. 
\subsection{Assume / Assert Instructions}

### 2013-06-14 tex/state.tex
Refined the definitions, added more math symbols

\section{System State}
The program state is represented using a path condition, a program location, a stack, a symbolic heap, and a symbolic store. The path condition is a collection of predicates over the program inputs that indicates constraints on the values of those inputs at the present location. The program location indicates the instruction to be executed presently. The symbolic heap is a mapping from heap locations symbolic objects. 
\paragraph{Heap Symbols}
Heap symbols are symbols which are created and destroyed in the process of performing heap operations. The dynamic nature of heap symbols distinguishes them from statically-created symbols like tbose found in the path condition. Heap symbols may be symbolic primitives, symbolic references, symbolic locations, or symbolic types.
\paragraph{Symbolic References}
Symbolic references are symbolic points-to relations. The symbolic reference has a state parameter that indicates whether the reference is uninitialized, non-null, or initialized. The uninitialized and non-null states indicate that the location pointed to by the reference has yet to be resolved. The non-null state reflects the additional constraint that the reference does not point to the null location. References in the initialized state are assosciated with constraints reflecting which location the reference points to and under what condition it points to that location. References point to one and only one location at a time, so the conditions must be mutually exclusive, yet collectively exhaustive.
\paragraph{Symbolic Locations}
Symbolic locations represent the locations of slots in the heap structure that may hold symbolic objects. Each symbolic location represents a unique slot on the symbolic heap. The constraints assosciated with symbolic locations reflect the uniqueness of each location. Each slot on the heap may contain a symbolic object. 
\paragraph{Symbolic Objects}
A symbolic object represents the contents of a heap slot. A symbolic object contains a symbolic type paired with a mapping from fields to heap symbols.
\paragraph{Symbolic Store}
The symbolic store is a mapping from heap symbols to symbolic value sets. The symbolic value set represents the values that may be assigned to the symbol, along with the constraints assosciated with each value. Taken together, the constraints in the abstract store represent a set of unique heaps common to the current program execution path. Compare this to the path condition, which contains constraints common to all the heaps in the abstract store.
\paragraph{Heap}
The symbolic heap is a mapping from symbolic locations to symbolic objects. Like the path condition, the symbolic heap contains heap state which is common to all heaps on the current execution path. Unlike the path condition, the symbolic heap does not contain any logical constraints.
\paragraph{Stack}
The Java Virtual Machine uses a system stack.

>>>>

\section{System State}
The program state is represented using a path condition, a program location, a stack, a symbolic heap, and a symbolic store. The path condition is a collection of predicates over the program inputs that indicates constraints on the values of those inputs at the present location. The program location indicates the instruction to be executed presently. The symbolic heap is a mapping from heap locations symbolic objects. 
\paragraph{Heap Symbols}
A heap symbol $\pi$ is a symbol which is created in the process of performing heap operations. The dynamic nature of heap symbols distinguishes them from statically-created symbols like those found in the path condition. Heap symbols may be symbolic primitives, symbolic references, symbolic locations, or symbolic types.
\paragraph{Symbolic References}
Symbolic references are symbolic points-to relations. The symbolic reference has a state parameter that indicates whether the reference is uninitialized, non-null, or initialized. The uninitialized and non-null states indicate that the location pointed to by the reference has yet to be resolved. The non-null state reflects the additional constraint that the reference does not point to the null location. References in the initialized state are associated with constraints reflecting which location the reference points to and under what condition it points to that location. References point to one and only one location at a time, so the conditions must be mutually exclusive, yet collectively exhaustive.
\paragraph{Symbolic Locations}
A symbolic location $h$ represents the index of a slot in the heap structure that holds a symbolic object. Each symbolic location represents a unique slot on the symbolic heap. There are two special symbolic locations null and non-null, which are never in the symbolic heap.
\paragraph{Symbolic Objects}
A symbolic object represents the contents of a heap slot. A symbolic object is characterized by a symbolic type, and contains a mapping from fields to heap symbols.
\paragraph{Constrained Symbol}
A constrained symbol $\psi$ is a symbol that assumes a value $\pi$ contingent upon the satisfiability of a constraint condition $\phi$.
\begin{equation}
\psi\models \phi\uparrow \Rightarrow\pi
\end{equation}
\paragraph{Symbolic Value Set}
A symbolic value set $\theta$ is a set of constrained symbols $\theta\colon \{\psi _1,\psi _2,...,\psi _n\}$, for which the constraints are mutually exclusive and collectively exhaustive.
\paragraph{Symbolic Store}
The symbolic store is a mapping from heap symbols to symbolic value sets $\mathbb{S}\colon \pi \mapsto \theta$. The abstract store represents a set of heaps common to the current program execution path. 
\paragraph{Heap}
The symbolic heap $\mathbb{H}$ is an indexed set of symbolic objects. Like the path condition, the symbolic heap contains heap state which is common to all heaps on the current execution path. 
\paragraph{Stack}
The Java Virtual Machine uses a system stack.
